---
title: "guesser_knower_test_battery_dogs"
author: "Lucrezia Lonardo"
date: "2025-02-27"
output: html_document
---

### Load libraries and custom functions
```{r}
rm(list=ls())
library(tidyverse)
library(ggplot2)
library(lme4)
library(summarytools)
library(car)
library(lmerTest)
library(forcats)
# source("functions/diagnostic_fcns.r")
# source("functions/glmm_stability.r")
# source("functions/boot_glmm.r")
```


### Import data

```{r}
xdata <- read.csv("data/test_phase.csv", header = TRUE) %>% 
  #  mutate(choice_letter = as.factor(choice_letter),
  #        condition = as.factor(condition),
  #        age_months = as.numeric(age_months)) %>% 
  #filter(!is.na(choice_binary)) %>%  
  droplevels()

which(is.na(xdata$choice_binary)) #double check for NAs
```
###Inspect data
```{r}
str(xdata)
```
###Descriptive stats
```{r}
subj.data<- xdata %>% 
  group_by(dog_id, condition) %>% 
  summarise(knower_pref=sum(choice_binary),
            trials=length(choice_binary),
            prop_knower_pref=knower_pref/trials)
```



### Plot performance in all conditions

```{r}
plot.data<- subj.data %>% 
  group_by(condition) %>% 
  summarise(avg_knower_pref=mean(prop_knower_pref, na.rm=T),
            se = sd(prop_knower_pref, na.rm = TRUE) / sqrt(n()),  # Standard Error
    ci_lower = avg_knower_pref - qt(0.975, df = n() - 1) * se,  # Lower 95% CI
    ci_upper = avg_knower_pref + qt(0.975, df = n() - 1) * se)   # Upper 95% CI


#Error bars show 95% confidence intervals; 
#asterisk indicates significance of the comparison with chance level (icpt only models)

ggplot(data=plot.data, aes(x=condition, y= avg_knower_pref)) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +  # Error bars
  geom_text(aes(x = 2, y = 0.69, label = "*"), size = 8) +
  geom_hline(yintercept = 0.5, lty=2) +
  coord_cartesian(ylim = c(0.2, 0.7))
```
### Boxplot 
```{r}
ggplot(data=subj.data, aes(x = condition, y = prop_knower_pref)) +
  geom_boxplot()  +
  geom_jitter(shape=20, position=position_jitter(0.1), alpha=.5)+
 #geom_line(aes(group = dog_id), alpha=0.3, lty=2) +
  ylim(c(0,1))+
  theme_bw()
  
```

### Icpt-only bin model 1) all experimental conditions (except control)
```{r}
#Subset the data to exclude guesser present
exp.data<-xdata %>% 
  filter(condition!="present")
```

 
```{r}
# Run model
icpt.mm1=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=exp.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```
```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(icpt.mm1) #overall, across all experimental conditions, dogs' prefer the knower
#slightly above chance level (p=0.019)

#transform logit scale values to probability values
confint_icpt.mm1 <- confint(icpt.mm1, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept <- logit_to_prob(fixef(icpt.mm1)[1])
confint_prob <- logit_to_prob(confint_icpt.mm1["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept, 3)))
print(paste("95% CI for probability:", round(confint_prob, 3)))
```
### Icpt-only bin model 2) back turned
```{r}
#Subset the data to keep only guesser back turned
bt.data<-xdata %>% 
  filter(condition=="back_turned")
```

 
```{r}
# Run model
icpt.mm2=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=bt.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(icpt.mm2)

#transform logit scale values to probability values
confint_icpt.mm2 <- confint(icpt.mm2, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept <- logit_to_prob(fixef(icpt.mm2)[1])
confint_prob <- logit_to_prob(confint_icpt.mm2["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept, 3)))
print(paste("95% CI for probability:", round(confint_prob, 3)))
```
### Icpt-only bin model 3) absent
```{r}
#Subset the data to keep only guesser absent
abs.data<-xdata %>% 
  filter(condition=="absent")
```

 
```{r}
# Run model
icpt.mm3=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=abs.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(icpt.mm3)
#dogs' performance not significantly different from chance in the abs condition

#transform logit scale values to probability values
confint_icpt.mm3 <- confint(icpt.mm3, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept3 <- logit_to_prob(fixef(icpt.mm3)[1])
confint_prob3 <- logit_to_prob(confint_icpt.mm3["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept3, 3)))
print(paste("95% CI for probability:", round(confint_prob3, 3)))
```
### Icpt-only bin model 4) looking away
```{r}
#Subset the data to keep only guesser absent
la.data<-xdata %>% 
  filter(condition=="looking_away")
```

 
```{r}
# Run model
icpt.mm4=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=la.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(icpt.mm4)
#dogs' performance not significantly different from chance in the looking away condition

#transform logit scale values to probability values
confint_icpt.mm4 <- confint(icpt.mm4, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept4 <- logit_to_prob(fixef(icpt.mm4)[1])
confint_prob4 <- logit_to_prob(confint_icpt.mm4["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept4, 3)))
print(paste("95% CI for probability:", round(confint_prob4, 3)))
```
# First trial only
### Icpt-only bin mod 1ft) all experimental conditions (except control)
```{r}
#create trial within condition variable
ft.data<-xdata %>% 
  group_by(dog_id, condition) %>%
  mutate(trial_within_cond = rank(trial, ties.method = "first")) %>%
  ungroup() %>% 
  filter(trial_within_cond==1)


#Subset the data to exclude guesser present
ft.exp.data<-ft.data %>% 
  filter(condition!="present")
```

 
```{r}
# Run model
ft.icpt.mm1=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=ft.exp.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(ft.icpt.mm1) #overall, across all experimental conditions, dogs did not prefer the knower above chance level from the first trial (Wald test of icpt p=0.199)

#LL: to be adapted
#transform logit scale values to probability values
confint_icpt.mm1 <- confint(icpt.mm1, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept <- logit_to_prob(fixef(icpt.mm1)[1])
confint_prob <- logit_to_prob(confint_icpt.mm1["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept, 3)))
print(paste("95% CI for probability:", round(confint_prob, 3)))
```
### Icpt-only bin mod 2ft) back turned
```{r}
#Subset the data to keep only guesser back turned
ft.bt.data<-ft.data %>% 
  filter(condition=="back_turned")
```

 
```{r}
# Run model
ft.icpt.mm2=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=ft.bt.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(ft.icpt.mm2) #In the bt condition, dogs preferred the knower slightly
#above chance level from trial 1

#LL: to be adapted
#transform logit scale values to probability values
confint_icpt.mm2 <- confint(icpt.mm2, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept <- logit_to_prob(fixef(icpt.mm2)[1])
confint_prob <- logit_to_prob(confint_icpt.mm2["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept, 3)))
print(paste("95% CI for probability:", round(confint_prob, 3)))
```
### Icpt-only bin mod 3ft) absent
```{r}
#Subset the data to keep only guesser absent
ft.abs.data<-ft.data %>% 
  filter(condition=="absent")
```

 
```{r}
# Run model
ft.icpt.mm3=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=ft.abs.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(ft.icpt.mm3)
#dogs' performance not significantly different from chance in the first trial of the 
#absent condition

#LL: to be adapted
#transform logit scale values to probability values
confint_icpt.mm3 <- confint(icpt.mm3, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept3 <- logit_to_prob(fixef(icpt.mm3)[1])
confint_prob3 <- logit_to_prob(confint_icpt.mm3["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept3, 3)))
print(paste("95% CI for probability:", round(confint_prob3, 3)))
```
### Icpt-only bin mod 4ft) looking away
```{r}
#Subset the data to keep only guesser absent
ft.la.data<-ft.data %>% 
  filter(condition=="looking_away")
```

 
```{r}
# Run model
ft.icpt.mm4=glmer(choice_binary ~ 1 +
                   (1|dog_id),
             data=ft.la.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

#Warning: Model is nearly unidentifiable: large eigenvalue ratio
 #- Rescale variables?
#LL: due to large amount of 0s?
```

```{r}
# Evaluate results
# Test if response probability is different from chance (0, on the logit scale)
summary(ft.icpt.mm4)
#dogs' performance not significantly different from chance in the first trial of
# the looking away condition

#LL: to be adapted
#transform logit scale values to probability values
confint_icpt.mm4 <- confint(icpt.mm4, method = "Wald")
logit_to_prob <- function(logit) exp(logit) / (1 + exp(logit))
prob_intercept4 <- logit_to_prob(fixef(icpt.mm4)[1])
confint_prob4 <- logit_to_prob(confint_icpt.mm4["(Intercept)", ])

print(paste("Estimated probability:", round(prob_intercept4, 3)))
print(paste("95% CI for probability:", round(confint_prob4, 3)))
```

### GLMM 01 - difference between conditions
```{r}
model.data <- xdata %>%
  mutate(condition = fct_recode(condition, 
                                "back turned" = "back_turned", 
                                "looking away" = "looking_away")) %>%
  mutate(condition = fct_relevel(condition, "present")) %>%  # Set "present" as reference
  mutate(z.age=as.vector(scale(age, center = TRUE, scale=TRUE)),
         z.trial=as.vector(scale(trial, center = TRUE, scale=TRUE)),
         condition.bt.c=
           as.vector(scale(as.numeric(condition==levels(as.factor(condition))[3]), center=TRUE, scale= FALSE)),
         condition.la.c=
           as.vector(scale(as.numeric(condition==levels(as.factor(condition))[4]), center=TRUE, scale= FALSE)),
         condition.abs.c=
           as.vector(scale(as.numeric(condition==levels(as.factor(condition))[2]), center=TRUE, scale= FALSE)))

#session nr. to be added once data is collected in session 2 and 3

levels(as.factor(model.data$condition)) #worked

```

```{r}
#Run the model
mm1_choice=glmer(choice_binary ~ condition + z.age + z.trial +
                (1+condition.abs.c+condition.bt.c+condition.la.c+z.age+z.trial|dog_id),
             data=model.data, family=binomial, 
            control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

round(summary(mm1_choice)$coefficients,2)

round(drop1(mm1_choice, test="Chisq"),3)

mm1_choice_drop1 <- round(drop1(mm1_choice, test="Chisq"),3) %>% 
  filter(!is.na(npar)) %>% 
  add_row(npar = rep(NA,1),  .before = 1)
mm1_choice_drop1
```
#LL: to be adapted from here

```{r}
# Check for collinearity
library(car)
xx=lm(opaque_choice ~ condition+z.trial+first_condition, data=first_choice_data)
vif(xx)
```
#### confidence intervals 
```{r}
mm1_choice.ci=boot.glmm.pred(model.res=mm1_choice, excl.warnings=F,
nboots=1000, para=T, n.cores="all-1", resol=1000, level=0.95)
```

#### model stability
```{r}
m.stab.fc <- glmm.model.stab(model.res = mm1_choice)
m.stab.fc$detailed$warnings
as.data.frame(round(m.stab.fc$summary[1:4, -1], 2))

m.stab.plot(round(m.stab.fc$summary[, -1], 2))
```


#### output table - first choice

```{r}
mm1_choice_output_table <-
  bind_cols(as.data.frame(summary(mm1_choice)$coeff),
            mm1_choice_drop1,
            mm1_choice.ci$ci.estimates,
            m.stab.fc$summary[1:4, -1],
            mm1_choice_aic_drop1_delta_df) %>%
  dplyr::select(
    Estimate,
    SE = `Std. Error`,
    Chi2 = LRT,
    df = npar,
    p = `Pr(Chi)`,
    LowerCI = X2.5.,
    UpperCI = X97.5.,
    min,
    max,
    delta_aic
  ) %>% #
  mutate(across(.cols = c(p), ~ format(round(.x, 3), nsmall = 3))) %>%
  mutate(across(.cols = c(Estimate:df), ~ format(round(.x, 2), nsmall = 2))) %>%
 mutate(across(.cols = c(LowerCI:max), ~ format(round(.x, 2), nsmall = 2))) %>%  #mutate(across(Chi2:p, ~replace_na(.x, "")))%>%
  mutate(p = replace(p, p == 0, "<0.001"))

write.csv(mm1_choice_output_table, file = "saves/mm1_choice_output_table.csv")
```

```{r}
save.image("./workspace/guesser_knower_workspace.RData")
```



